---
title: "Aggregated data plugins"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aggregated_data_plugins}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Exclusion criteria manager

### Description

- **Version** : 0.0.1
- **Libraries** : none
- **Plugins required to be executed before** : none

### UI code

```{r, eval = FALSE}
temp <- function(){

    # Create our dictionnary
    new_words <- tibble::tribble(~language, ~reference_word, ~translated_word,
        "EN", "add_exclusion_criterion", "Add an exclusion criterion",
        "FR", "add_exclusion_criterion", "Ajouter un critère d'exclusion",
        "EN", "exclusion_criteria_management", "Exclusion criteria management",
        "FR", "exclusion_criteria_management", "Gestion des critères d'exclusion"
    )
    
    # Render UI
    tagList(
        shiny.fluent::Text(variant = "large", translate(language, "add_exclusion_criterion", new_words), block = TRUE),
        shiny.fluent::Stack(horizontal = TRUE, tokens = list(childrenGap = 20),
            make_textfield(language = language, ns = ns, label = "name", id = "name_%group_id%_%study_id%", width = "300px"),
            div(shiny.fluent::PrimaryButton.shinyInput(ns("add_%group_id%_%study_id%"), translate(language, "add", r$words)), style = "margin-top:38px;")
        ),
        br(),
        shiny.fluent::Text(variant = "large", translate(language, "exclusion_criteria_management", new_words), block = TRUE),
        div(
            DT::DTOutput(ns("datatable_%group_id%_%study_id%")),
            shiny.fluent::PrimaryButton.shinyInput(ns("save_%group_id%_%study_id%"), translate(language, "save", r$words))
        )
    ) -> result
    
    result
}

temp()
```

### Server code

```{r, eval = FALSE}
##########################################
# Translations                           #
##########################################

# Create our dictionnary
new_words <- tibble::tribble(~language, ~reference_word, ~translated_word,
    "EN", "exclusion_criterion_added", "New exclusion criterion added",
    "FR", "exclusion_criterion_added", "Nouveau critère d'exclusion ajouté",
    "EN", "delete_exclusion_criterion", "Delete an exclusion criterion",
    "FR", "delete_exclusion_criterion", "Supprimer un critère d'exclusion",
    "EN", "delete_exclusion_criterion_subtext", "Are you sure you want to delete this exclusion criterion ?",
    "FR", "delete_exclusion_criterion_subtext", "Etes-vous sûr de vouloir supprimer ce critère d'exclusion ?",
    "EN", "exclusion_criterion_deleted", "Exclusion criterion deleted",
    "FR", "exclusion_criterion_deleted", "Critère d'exclusion supprimé"
)

##########################################
# Load current exclusion criteria        #
##########################################

plugins_load_%group_id%_%study_id% <- function(r){

    # Load exclusion criteria
    sql <- "SELECT id, value, creator_id, datetime FROM modules_elements_options WHERE deleted IS FALSE AND group_id = %group_id% AND study_id = %study_id% AND category = 'aggregated' AND name = 'name'"
    exclusion_criteria <- DBI::dbGetQuery(r$db, sql)
    
    # Load display orders
    sql <- "SELECT link_id, value_num FROM modules_elements_options WHERE deleted IS FALSE AND group_id = %group_id% AND study_id = %study_id% AND category = 'aggregated' AND name = 'display_order'"
    display_orders <- DBI::dbGetQuery(r$db, sql) %>% dplyr::select(id = link_id, display_order = value_num)
    
    # Merge the two tables
    # Reset display_order column (if we have display orders 1, 2 & 4 in database - if on criterion has been deleted - we will have 1, 2 & 3)
    exclusion_criteria <- exclusion_criteria %>% dplyr::left_join(display_orders, by = "id") %>% dplyr::relocate(display_order, .after = "value") %>% dplyr::arrange(display_order)
    
    # Get creator name
    exclusion_criteria <- 
        exclusion_criteria %>% 
        dplyr::left_join(
            isolate(r$users) %>% dplyr::transmute(creator_id = id, creator_name = paste0(firstname, " ", lastname)),
            by = "creator_id") %>%
        dplyr::relocate(creator_name, .after = "display_order") %>% dplyr::select(-creator_id)
        
    r$plugins_load_%group_id%_%study_id% <- exclusion_criteria
}

plugins_load_%group_id%_%study_id%(r)

##########################################
# Add a new exclusion criterion          #
##########################################

observeEvent(input$add_%group_id%_%study_id%, {

    tryCatch({
    
        new_name <- input$name_%group_id%_%study_id%
        
        if (length(new_name) == 0) shiny.fluent::updateTextField.shinyInput(session, "name_%group_id%_%study_id%", errorMessage = translate(language, paste0("provide_valid_name"), r$words))
        else shiny.fluent::updateTextField.shinyInput(session, "name_%group_id%_%study_id%", errorMessage = NULL)
        
        req(length(new_name) > 0)
        
        sql <- "SELECT DISTINCT(value) FROM modules_elements_options WHERE deleted IS FALSE AND group_id = %group_id% AND study_id = %study_id% AND name = 'name'" 
        distinct_values <- DBI::dbGetQuery(r$db, sql) %>% dplyr::pull() %>% tolower()
          
        if (tolower(new_name) %in% distinct_values) show_message_bar(output, 2, "name_already_used", "severeWarning", language)
        req(tolower(new_name) %not_in% distinct_values)
        
        last_row <- get_last_row(r$db, "modules_elements_options")
        datetime <- as.character(Sys.time())
        
        # Insert new exclusion criterion in database
        
        sql <- glue::glue_sql("INSERT INTO modules_elements_options(id, group_id, study_id, category, name, value, creator_id, datetime, deleted)
            SELECT {last_row + 1}, %group_id%, %study_id%, 'aggregated', 'name', {new_name}, {r$user_id}, {datetime}, FALSE", .con = r$db)
        query <- DBI::dbSendStatement(r$db, sql)
        DBI::dbClearResult(query)
        
        # Insert also its display order
        sql <- glue::glue_sql(paste0("SELECT COALESCE(MAX(value_num), 0) FROM modules_elements_options WHERE deleted IS FALSE AND group_id = %group_id% AND study_id = %study_id%",
            " AND category = 'aggregated' AND name = 'display_order'"), .con = r$db)
        last_display_order <- DBI::dbGetQuery(r$db, sql) %>% dplyr::pull()
        
        sql <- glue::glue_sql("INSERT INTO modules_elements_options(id, group_id, study_id, link_id, category, name, value_num, creator_id, datetime, deleted)
            SELECT {last_row + 2}, %group_id%, %study_id%, {last_row + 1}, 'aggregated', 'display_order', {last_display_order + 1}, {r$user_id}, {datetime}, FALSE", .con = r$db)
        query <- DBI::dbSendStatement(r$db, sql)
        DBI::dbClearResult(query)
        
        # Reload data
        plugins_load_%group_id%_%study_id%(r)
        
        # Reset textfield
        shiny.fluent::updateTextField.shinyInput(session, "name_%group_id%_%study_id%", value = NULL)
        
        show_message_bar(output, 1, translate(language, "exclusion_criterion_added", new_words), "success", language)
    
    },
    error = function(e) if (nchar(e[1]) > 0) report_bug(r = r, output = output, error_message = "error_run_plugin_server_code", 
      error_name = "%group_id% - run server code", category = "Error", error_report = toString(e), language = language),
    warning = function(w) if (nchar(w[1]) > 0) report_bug(r = r, output = output, error_message = "error_run_plugin_server_code", 
      error_name = "%group_id% - run server code", category = "Warning", error_report = toString(w), language = language))
})

##########################################
# Management datatable                   #
##########################################

col_names <- c("ID", "Name", "Display order", "Creator", "Datetime", "Action")
sortable_cols <- c("id", "value", "display_order", "creator_name", "datetime")
centered_cols <- c("id", "datetime", "display_order", "action", "creator_name")
column_widths = c("id" = "100px", "datetime" = "180px", "action" = "80px", "display_order" = "100px", "creator_name" = "100px", "name" = "400px")
searchable_cols <- c("value", "datetime", "creator_name")


observeEvent(r$plugins_load_%group_id%_%study_id%, {

    tryCatch({
    
        # Get page_id for dropdowns & delete button
        page_id <- id
        
        # Add dropdown for display order & delete buttons
        
        options <- list()
        if (nrow(r$plugins_load_%group_id%_%study_id%) > 0){
            
            options <- convert_tibble_to_list(data = r$plugins_load_%group_id%_%study_id% %>% dplyr::mutate(n = 1:dplyr::n()), key_col = "n", text_col = "n")
            
            # If this is not an update of the dropdowns
            
            if (length(unique(r$plugins_load_%group_id%_%study_id%$display_order)) == nrow(r$plugins_load_%group_id%_%study_id%)){
                r$plugins_load_%group_id%_%study_id% <- r$plugins_load_%group_id%_%study_id% %>% dplyr::arrange(display_order) %>% dplyr::mutate(n = 1:dplyr::n())} 
            else r$plugins_load_%group_id%_%study_id% <- r$plugins_load_%group_id%_%study_id% %>% dplyr::mutate(n = display_order)
            
            data_temp <- r$plugins_load_%group_id%_%study_id% %>%
                dplyr::rowwise() %>%
                dplyr::mutate(
                    display_order = as.character(
                        div(
                            shiny.fluent::Dropdown.shinyInput(ns(paste0("dropdown_%group_id%_%study_id%_", id)),
                                options = options, value = as.integer(n),
                                onclick = paste0("Shiny.setInputValue('", page_id, "-dropdown_updated', '", paste0("dropdown_%group_id%_%study_id%_value_", id), "', {priority: 'event'})"),
                                style = "width:120px;"
                            )
                        )
                    ),
                    action = as.character(
                        div(
                            shiny::actionButton(ns(paste0("delete_%group_id%_%study_id%_", id)), "", icon = icon("trash-alt"),
                            onclick = paste0("Shiny.setInputValue('", page_id, "-deleted_pressed_%group_id%_%study_id%', this.id, {priority: 'event'})"))
                        )
                    )
                ) %>%
                dplyr::select(-n)
        }
        else data_temp <- tibble::tibble()
    
        # Render datatable
        render_datatable(
            data = data_temp,
            output = output,
            r = r,
            ns = ns,
            language = language,
            output_name = "datatable_%group_id%_%study_id%",
            col_names = col_names,
            page_length = 20,
            sortable_cols = sortable_cols,
            centered_cols = centered_cols,
            column_widths = column_widths,
            filter = TRUE,
            searchable_cols = searchable_cols
        )
        
        # Make an observer by dropdown
        sapply(r$plugins_load_%group_id%_%study_id% %>% dplyr::pull(id), function(id){
        
            observeEvent(input[[paste0("dropdown_%group_id%_%study_id%_", id)]], {
            
                new_value <- input[[paste0("dropdown_%group_id%_%study_id%_", id)]]
                r$plugins_load_%group_id%_%study_id%[[which(r$plugins_load_%group_id%_%study_id%["id"] == id), "display_order"]] <- new_value
            })
        })
    },
    error = function(e) if (nchar(e[1]) > 0) report_bug(r = r, output = output, error_message = "error_run_plugin_server_code", 
      error_name = "%group_id% - run server code", category = "Error", error_report = toString(e), language = language),
    warning = function(w) if (nchar(w[1]) > 0) report_bug(r = r, output = output, error_message = "error_run_plugin_server_code", 
      error_name = "%group_id% - run server code", category = "Warning", error_report = toString(w), language = language))
})

##########################################
# Change display order                   #
##########################################

observeEvent(input$save_%group_id%_%study_id%, {
    duplicates_display_order <- r$plugins_load_%group_id%_%study_id% %>% 
        dplyr::group_by(display_order) %>% dplyr::summarize(n = dplyr::n()) %>% dplyr::filter(n > 1) %>% nrow()
        
    if (duplicates_display_order > 0) show_message_bar(output, 1, "modif_display_order_duplicates", "severeWarning", language)
    
    req(duplicates_display_order == 0)
    
    # Delete data from table
    ids_to_del <- r$plugins_load_%group_id%_%study_id% %>% dplyr::pull(id)
    DBI::dbSendStatement(r$db, paste0("DELETE FROM modules_elements_options WHERE link_id IN (", paste(ids_to_del, collapse = ","), ")")) -> query
    DBI::dbClearResult(query)
    
    # Append data to table
    last_row <- get_last_row(r$db, "modules_elements_options")
    
    new_data <- r$plugins_load_%group_id%_%study_id% %>%
        dplyr::transmute(group_id = %group_id%, study_id = %study_id%, patient_id = NA_integer_, link_id = id, category = "aggregated", name = "display_order", 
            value = NA_character_, value_num = display_order, creator_id = r$user_id, datetime, deleted = FALSE) %>%
        dplyr::mutate(id) %>% dplyr::relocate(id)
    new_data$id <- seq.int(nrow(new_data)) + last_row
    
    DBI::dbAppendTable(r$db, "modules_elements_options", new_data)
    
    # Notification to the user
    show_message_bar(output, 2, "modif_saved", "success", language)
})

##########################################
# Delete a row                           #
##########################################
    
# Delete button is pressed
observeEvent(input$deleted_pressed_%group_id%_%study_id%, r$delete_dialog_%group_id%_%study_id% <- TRUE)

# Rendering react output
observeEvent(r$delete_dialog_%group_id%_%study_id% , {
    output$delete_confirm <- shiny.fluent::renderReact({
        dialogContentProps <- list(
            type = 0,
            title = translate(language, "delete_exclusion_criterion", new_words),
            closeButtonAriaLabel = "Close",
            subText = translate(language, "delete_exclusion_criterion_subtext", new_words)
        )
        shiny.fluent::Dialog(
            hidden = !r$delete_dialog_%group_id%_%study_id%,
            onDismiss = htmlwidgets::JS(paste0("function() { Shiny.setInputValue('hide_dialog_%group_id%_%study_id%', Math.random()); }")),
            dialogContentProps = dialogContentProps,
            modalProps = list(),
            shiny.fluent::DialogFooter(
                shiny.fluent::PrimaryButton.shinyInput(ns("delete_confirmed_%group_id%_%study_id%"), text = translate(language, "delete", r$words)),
                shiny.fluent::DefaultButton.shinyInput(ns("delete_canceled_%group_id%_%study_id%"), text = translate(language, "dont_delete", r$words))
            )
        )
    })
})

# Whether to close or not delete dialog box
observeEvent(input$hide_dialog_%group_id%_%study_id%, r$delete_dialog_%group_id%_%study_id% <- FALSE)
observeEvent(input$delete_canceled_%group_id%_%study_id%, r$delete_dialog_%group_id%_%study_id% <- FALSE)

# When the delete is confirmed
observeEvent(input$delete_confirmed_%group_id%_%study_id%, {
    
    # Get value of deleted row
    row_deleted <- as.integer(substr(input$deleted_pressed_%group_id%_%study_id%, nchar(paste0(id, "-delete_%group_id%_%study_id%_")) + 1, nchar(input$deleted_pressed_%group_id%_%study_id%)))
    
    # Delete row in database
    sql <- glue::glue_sql("UPDATE modules_elements_options SET deleted = TRUE WHERE id = {row_deleted} OR link_id = {row_deleted}", .con = r$db)
    query <- DBI::dbSendStatement(r$db, sql)
    DBI::dbClearResult(query)
    
    # Change display orders, depending on the display order of deleted row
    sql <- glue::glue_sql("SELECT value_num FROM modules_elements_options WHERE link_id = {row_deleted}", .con = r$db)
    display_order_deleted <- DBI::dbGetQuery(r$db, sql) %>% dplyr::pull()
    sql <- glue::glue_sql(paste0("UPDATE modules_elements_options SET value_num = value_num - 1",
        " WHERE deleted IS FALSE AND group_id = %group_id% AND study_id = %study_id% AND category = 'aggregated' AND name = 'display_order' AND value_num > {display_order_deleted}"), .con = r$db)
    query <- DBI::dbSendStatement(r$db, sql)
    DBI::dbClearResult(query)
    
    # Close dialog box
    r$delete_dialog_%group_id%_%study_id% <- FALSE
    
    # Reload r variable
    plugins_load_%group_id%_%study_id%(r)
    
    # Notification to user
    show_message_bar(output = output, id = 3, translate(language, "exclusion_criterion_deleted", new_words), type ="severeWarning", language = language)
})
```

## Flowchart creator

### Description
### UI code
### Server code

## Data cleaning plugin

### Description
### UI code
### Server code

## Features creation plugin

### Description
### UI code
### Server code

## Features visualization plugin

### Description
### UI code
### Server code

## Machine learning models plugin

### Description
### UI code
### Server code

## Extract CSV plugin

### Description
### UI code
### Server code

## Report creation plugin

### Description
### UI code
### Server code

## Study guidelines plugin

### Description
### UI code
### Server code