---
title: "Developper help"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dev_data_management}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## App database

## Users

## Data management

### Data sources

A data source can be a data warehouse, a CSV file etc.

To **create a data source**, the name must be unique. You can add a short description, which is optional.
The thesaurus are attached to the data source later, in the thesaurus section.

You can **edit** name & description by double-clicking on the field, delete a data source.

### Datamarts

A datamart is a **data access to a part of a data warehouse**. It is often the screening criteria of a study (eg : all patients who received Meropenem in the ICU unit of my hospital, between 2021-01 & 2021-06).

To **create a datamart**, the name must be unique. You can add a short description, which is optional.
Choose a data source : it links the thesaurus (one thesaurus is attached to one or multiple data source(s)) and the datamart.

On the **management page**, you can edit name & description by double-clicking on the field, edit data source by changing the value of the dropdown. The other fields cannot be updated. In the action column, you can delete a datamart, edit options or edit code.

On the **Edit code page**, you can edit the code that creates the datamart with the ShinyAce editor.

The code has to be as follows :

```{r eval = FALSE}
# Connection to the database, from where we extract data
con <- DBI::dbConnect(RPostgres::Postgres(), dbname = "mimic-iv", host = "localhost",
  port = 5432, user = "admin", password = "admin")

# Create a patients function which, when executed, gets the patients data
patients <- function(){
  DBI::dbGetQuery(con, paste0("SELECT * FROM mimic_core.patients LIMIT 10")) %>%
  dplyr::select(patient_id = subject_id, gender, age = anchor_age, dod)
}

# Run import_datamart function, with patients function as data argument
import_datamart(output = output r = r, datamart_id = %datamart_id%, data = patients(), type = "patients", 
  save_as_csv = TRUE, rewrite = FALSE, language = "EN")

# Close connection
DBI::dbDisconnect(con)
```

There's **five data variables** to create : `patients`, `stays`, `labs_vitals`, `text` and `orders`.

For each data variable, you have to :

- create a function, containing code that allows to get data
- run `import_datamart` function, with the function as `data` argument

The advantage to store the code that allows to get data in a function is that this code is not run each time a user uses the datamart.
If you set the argument `save_as_csv` to TRUE (and `rewrite` to FALSE), then the code is run only the first time the script is excecuted.

You can **Run the code**, with Run code button. It executes all the R code contained in the editor.

Note that you can use `%datamart_id%` : it will be replaced by the current datamart_id before executing the code.

See `import_datamart` documentation for more informations (`?import_datamart`).

On the **options page**, you can choose if the users are allowed to see individual patients data, or just aggregated data. It can be useful to have frequent statistics about a group of patients without having to see individual data : eg a weekly updated datamart with bed occupancy of a hospital unit.

You have to choose which users will have access to this datamart.

### Studies

A study is a project using a datamart. One datamart can contains several studies. Each study contains all patients of the datamart.

To **create a study**, the name must be unique. You can add a short description, which is optional.
You have to choose the datamart, from which the data comes.
You have to choose a patient-level data module family & an aggregated data module family.

The page **Patient-level data** allows a user to have access to individual patient data. This page **works with modules**, which are subpages created by a user.
In a module, a user **chooses which items** of the thesaurus will be displayed (eg Heart rate & Respiratory rate), in **which form** (eg in a timeline).
These modules are **grouped under module families**, so that a module created by one user can be re-used by others (eg MIMIC-IV default module family).

The page **Aggregated data** allows a user to have access to patients grouped data. This pages also works with modules, with the same principle as Patient-level data.

On the **management page**, you can edit name & description by double-clicking on the field, edit datamart, patient-level data module family & aggregated data module-family by modifying the value of the dropdown.
You can delete a study, edit its options.

You can choose who has access to a study. 

When a study is created, it automatically **creates three subsets** :

- All patients : this subset contains all patients of the datamart
- Included patients : it will be used to save patients included in the study
- Excluded patients

The code to generate All patients subset is added in the subset code (see next section).

### Subsets

A subset is a set of patients picked in a study. All patients, included & excluded patients subsets are created by default and are not deletable.

To **create a subset**, the name must be unique. You can add a short description, which is optional.
You have to choose a study, from which the patients comes.

You can **edit** name & description by double-clicking on the field, edit study by modifying the value of the dropdown.
You can delete a subset (except All / Included / Excluded patients subsets), edit options : add or delete patients from the subset.

On the **Edit code page**, you can edit the code that adds patients in a subset with the ShinyAce editor.

The code has to be as follows :

```{r eval = FALSE}
# Run code that allows access to datamart data
# After running this function, data is accessible with r$... variables (eg r$patients for patients)
run_datamart_code(output = output, r = r, datamart_id = %datamart_id%)

# We create a patients dataframe, containing patients we want to include in this subset
# We can add some filters here (eg r$patients %>% dplyr::filter(age > 18) to get patients with an age superior to 18 y-old)
patients <- r$patients %>% dplyr::select(patient_id) %>% dplyr::mutate_at('patient_id', as.integer)

# We finally run subset_add_patients function, with our patients datafarme as patients argument
# It will add our patients to the subset specified with subset_id
# Note that if erase is set to FALSE, it will not add patients as long as there are already some patients in this subset
subset_add_patients(output = output, r = r, patients = patients, subset_id = %subset_id%, erase = FALSE)
```

It is the same principle here than developped in datamarts section : you can use `%datamart_id%` & `%subset_id%` to access to current datamart's & subset's IDs.

See `run_datamart_code` & `subset_add_patients` documentation for more informations (`?run_datamart_code` or `?subset_add_patients`).

### Thesaurus

A thesaurus contains concepts used in the data warehouse (eg heart rate, respiratory rate, medication etc).

To **create a thesaurus**, the name must be unique. You can add a short description, which is optional.
You need to choose one or several data sources, to which the thesaurus will be linked.

On the **management page**, you can edit name & description by double-clicking on the field, edit data source by modifying the value of the dropdown.
You can delete a thesaurus, edit code, show thesaurus items.

On the **Edit code page**, you can edit the code that creates thesaurus with the ShinyAce editor. It is the same principle as the datamart code.

The code has to be as follows :

```{r eval = FALSE}
# Connection to the database, from where we extract data
con <- DBI::dbConnect(RPostgres::Postgres(), dbname = "mimic-iv", host = "localhost",
  port = 5432, user = "admin", password = "admin")

# Create a thesaurus function which, when executed, gets the thesaurus data
thesaurus <- function(){
  DBI::dbGetQuery(con, "SELECT itemid AS item_id, label AS name, category, unitname AS unit FROM mimic_icu.d_items") %>% 
  tibble::as_tibble() %>% dplyr::transmute(item_id, name, display_name = "", category, unit)
}

# Run import_thesaurus function, with thesaurus function as thesaurus argument
import_thesaurus(output = output, r = r, thesaurus_id = %thesaurus_id%, thesaurus = thesaurus(), language = "EN")

# Close connection
DBI::dbDisconnect(con)
```

Note that you can use `%thesaurus_id%` : it will be replaced by the current thesaurus_id before executing the code.

See `import_thesaurus` documentation for more informations (`?import_thesaurus`).

On the **Thesaurus items page**, you can display thesaurus items by clicking on the table icon, on action column of thesaurus management.
You can edit item name, display name, category & unit.

The **display name** is the named used by default in the figures, when the item is displayed on Patient-level data or Aggregated data (eg : HR for heart rate).
The **category** is useful to search an item (eg : Haemodynamics for Heart rate, Systolic arterial blood pressure, Noradrenaline etc).
You can edit an item **unit name**. The unit conversion is not yet available.

## Modules & plugins

### Plugins

### Modules

## Log